Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-29 draft/paper1_jenny.tex
Edit basic data reduction

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

@@

    The full details of the HSC data processing can be found in \citet{BoschInPrep}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
    the response curves of SDSS-$i$ and HSC-$i$ filters.}
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

@@

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
    The spec-z quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    \update{
    Objects without a spectroscopic redshift are matched with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    We keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for centrals in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    }
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    Before we can define our mass-complete sample of central galaxies required for 
    our analysis, we describe our one-dimensional photometric analysis 
    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
    We then define the final sample in \S \ref{sec:final}.

@@

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    Although \cmodel{} tends to underestimate the total flux for bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipeInPrep}).

>>>>

    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

@@

    The full details of the HSC data processing can be found in \citet{Bosch2017}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
    We therefore made a conservative selection of initial sample of massive galaxies
    with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
    between the response curves of SDSS-$i$ and HSC-$i$ filters.}
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

@@

    Here we limit our study to the very high-mass end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} galaxy cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    Objects without a spectroscopic redshift are matched with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    We keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for centrals in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. and the GAMA survey provides additional $14$\% of spec-$z$.
    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Evolution in structure and stellar population properties can be largely 
    ignored.  
    At both lower and higher redshift, the completeness of spec-$z$ sample starts 
    to decline.  
    Also for bright galaxies at lower redshift, the over-subtraction of background 
    becomes a more serious issue. 
    Before we can define our mass-complete sample of massive galaxies required for 
    our analysis, we describe our one-dimensional photometric analysis 
    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
    We then define the final sample in \S \ref{sec:final}.

@@

    We use the broadband Spectral Energy Distributions (SEDs) fitting 
    (see \citealt{Walcher2011} for a recent review) code 
    \texttt{iSEDFit}\footnote{http://www.sos.siena.edu/~jmoustakas/isedfit/} 
    (\citealt{Moustakas13}) to estimate the average \m2l{} and $k$-corrections using
    5-band HSC \cmodel{} fluxes.
    Although \cmodel{} tends to underestimate the total flux for bright, extended 
    objects, it can still yield accurate \emph{average} colors thanks to the 
    forced-photometry method that takes the PSF convolution into account
    (e.g. \citealt{SynPipe}).
